---
title: "Experiment 7 Bacteria"
author: "Brianne"
date: "15.11.2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/briannepalmer/Library/CloudStorage/OneDrive-Personal/Leaf Fossilization Experiment 7/Experiment 7")
```

required Libraries

```{r}
library(ecodist)
library(tidyverse)
library(vegan)
library(data.table)
```

Load bacteria OTU data and create a new column for relative abundance, use relative abundance values throughout

```{r}
diatoms <- fread("/Users/briannepalmer/Downloads/NymphaeaNuphar 18S Analysis MrDNA/analysisfiles/100722BP1SSU-zotus.fa.mapping.txt")

diatoms.fix  <- separate(data = diatoms, col = V3, into = c("sp", "kingdom", "phylum", "class", "order", "family", "genus", "species", "superkingdom", "subphylum"), sep = ";")

diatoms.fix  <- separate(data = diatoms.fix, col = V1, into = c("SampleID", "n1", "n2", "n3", "n4", "n5", "n6", "n7", "n8", "n9", "n10"), sep = ":")

diatoms <- diatoms.fix %>% dplyr::select(SampleID, V2, kingdom, phylum, class, order, family, genus)


fwrite(diatoms, file = "waterlilies_.txt")
#fwrite(experiment7, file = "experiment7.txt")


diatoms <- diatoms  %>% dplyr::rename(OTU = V2)
diatoms <- diatoms %>%  add_count(OTU) %>% filter(kingdom == "k__eukaryota")
diatoms.gp <- diatoms %>% group_by(SampleID, OTU) %>% summarize(n = sum(n))  
diatoms.gp <- diatoms.gp %>% mutate(rel = n / sum(n)) 

#Load metadata file
SampleID <- unique(diatoms$SampleID)
plant <- c("nuphar", "nuphar", "nuphar", "nuphar", "nuphar", "nuphar", "nymphaea", "nymphaea", "nymphaea", "nymphaea", "nymphaea", "nymphaea")
Location <- c("Bottom", "Bottom", "Bottom", "Top", "Top", "Top", "Bottom", "Bottom", "Bottom", "Top", "Top", "Top")
Replicate <- c("R1", "R2", "R3","R1", "R2", "R3","R1", "R2", "R3","R1", "R2", "R3")
Treatment <-c("nuphar_bottom", "nuphar_bottom", "nuphar_bottom", "nuphar_top", "nuphar_top", "nuphar_top", "nymphaea_bottom", "nymphaea_bottom", "nymphaea_bottom", "nymphaea_top", "nymphaea_top", "nymphaea_top")

metadata <- data.frame(SampleID, Treatment, plant, Replicate, Location)

```

Transpose the 'bacteria' file so the OTUs are columns, make all OTU values numeric and make NAs = 0. Then group by SampleID to get 30 lines and create a new file with the OTU values only

```{r}
diatoms.t <- diatoms.gp %>% pivot_wider(names_from =OTU, values_from = rel)
diatoms.t[c(3:212)] <- sapply(diatoms.t[c(3:212)],as.numeric)
diatoms.t[c(3:212)][is.na(diatoms.t[c(3:212)])] <-0
diatoms.t <- diatoms.t %>% group_by(SampleID) %>% summarize_all(sum)
otu.only <- diatoms.t[3:212]
```

make bray-curtis matrix

```{r}
otu.bray <- vegdist(otu.only, method = "bray")# dissimilarity matrix using bray-curtis distance indices
```

Calculate PCoA values

```{r}
pcoaVS <- pco(otu.bray, negvals = "zero", dround = 0) # if negvals = 0 sets all negative eigenvalues to zero
```

Make dataframe for plot with vectors and metadata

```{r}
pcoa1 = pcoaVS$vectors[,1] # adds the points of the NMDS 1 dimmension
pcoa2 = pcoaVS$vectors[,2] # adds the points of the NMDS 2 dimmension

MDS = data.frame(pcoa1 = pcoa1, pcoa2 = pcoa2)
MDS = cbind(MDS, metadata)

```

Make plot

```{r}
set.seed(12345)

ggplot(MDS, aes(x = pcoa1, y = pcoa2, color = Location, shape = plant)) + geom_point(size =3) + 
  theme_bw()
```

Look for statistial differences in community composition using a PERMANOVA (adonis function in 'vegan')

```{r}
set.seed(12345)
adonis2(otu.only ~ Treatment, metadata) # 0.02 (for eukaryotes)
adonis2(otu.only ~ plant, metadata) # 0.024 (for eukaryotes)
adonis2(otu.only ~ Location, metadata) # 0.047 (for eukaryotes)

```

When we have multiple comparisons, adonis doesn't tell us which groups are different from each other so we can use a pairwise PERMANOVA. Since we are comparing muliple groups, we need to look at the adjusted p-value to determine significance.

