---
title: "WaterLilies TopBottom"
output: html_document
date: "2023-01-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/briannepalmer/Library/CloudStorage/OneDrive-Personal/LeafFossilization/Leaf Fossilization Experiments_3_4_7_8/Experiment 7")
```

This is the R code for all the analyses performed for Experiment 7 (water lilies, top and bottom). If there are questions about the code please contact Brianne Palmer (bpalmer[at]uni-bonn.de)

There are several packages required to perform these analyses and create the figures. There are probably easier ways to do some of this, but if the code works, why change it?
```{r, Load Libraries}
library(phyloseq)
library(plyr)
library(data.table)
library(tidyverse)
library(vegan)
library(ecodist)
library(patchwork)
library(RColorBrewer)
library(ape)
library(microbiome)
library(microbiomeMarker)
library(ampvis2)
library(ggpubr)
library(ggvenn)
library(indicspecies)
library(ggpattern)
library(rstatix)
library(ggrepel)
```

Load Data
```{r}
S18 <- fread("/Users/briannepalmer/Library/CloudStorage/OneDrive-Personal/LeafFossilization/Dataframes_to_merge/experiment7_18S.csv")

S16 <- fread("/Users/briannepalmer/Library/CloudStorage/OneDrive-Personal/LeafFossilization/Dataframes_to_merge/experiment7_16S.csv")

ITS <- fread("/Users/briannepalmer/Library/CloudStorage/OneDrive-Personal/LeafFossilization/Dataframes_to_merge/experiment7_ITS.csv")
```

```{r}
# the metadata 
SampleID <- c("NuBotR1", "NuBotR2", "NuBotR3", "NuTopR1", "NuTopR2", "NuTopR3", "NyBotR1", "NyBotR2", "NyBotR3", "NyTopR1", "NyTopR2", "NyTopR3")
Location <-c("buried", "buried", "buried", "floating", "floating", "floating", "buried", "buried", "buried", "floating", "floating", "floating")
plant <- c("Nuphar", "Nuphar", "Nuphar", "Nuphar", "Nuphar", "Nuphar", "Nymphaea", "Nymphaea", "Nymphaea", "Nymphaea", "Nymphaea", "Nymphaea")
treatment <- c("NuBot", "NuBot", "NuBot", "NuTop", "NuTop", "NuTop", "NyBot", "NyBot", "NyBot", "NyTop", "NyTop", "NyTop")

metadata <- data.frame(SampleID, Location, plant, treatment)
```

```{r}
x18 <- seq(1:4161)
x16 <- seq(1:3997)
xITS <- seq(1:630)
```

```{r}
ASV.16 <- as.vector(paste0("ASV", x16))
ASV.ITS <- as.vector(paste0("ASV", xITS))
S16$ASV <- ASV.16
ITS$ASV <- ASV.ITS
```

```{r}
# make new columns with count and relative abundance 
S18[,c(2:13)] <-sweep(S18[,c(2:13)], 2, colSums(S18[,c(2:13)]), `/`)
S18$n <- rowSums(S18[ , c(2:13)], na.rm=TRUE)

S18.e <- S18 %>% filter(kingdom %in% c("Eukaryota", "Eukaryota:mito", "Eukaryota:plas"))
ASV.18.e <- as.vector(paste0("ASV", seq(1:54)))
S18.e$ASV <- ASV.18.e

S18.p <- S18 %>% filter(kingdom %in% c("Bacteria", "Archaea"))
ASV.18.p <- as.vector(paste0("ASV", seq(1:2231)))
S18.p$ASV <- ASV.18.p

S16[,c(2:13)] <-sweep(S16[,c(2:13)], 2, colSums(S16[,c(2:13)]), `/`)
S16$n <- rowSums(S16[ , c(2:13)], na.rm=TRUE)
ITS[,c(2:13)] <-sweep(ITS[,c(2:13)], 2, colSums(ITS[,c(2:13)]), `/`)
ITS$n <- rowSums(ITS[ , c(2:13)], na.rm=TRUE)
```

Make another table with the ASVs as columns, this is necessary for the PCOA

```{r, PCOA for 16S}
transformed.16 <- t(S16[,c(2:13)])
colnames(transformed.16) <- ASV.16
transformed.16[is.na(transformed.16)] <-0
transformed.16[c(1:3997)] <- sapply(transformed.16[c(1:3997)],as.numeric)

otu.bray.16 <- vegdist(transformed.16, method = "bray")
pcoaVS.16 <- ecodist::pco(otu.bray.16, negvals = "zero", dround = 0)

pcoa1.16 = pcoaVS.16$vectors[,1] # adds the points of the NMDS 1 dimmension
pcoa2.16 = pcoaVS.16$vectors[,2] # adds the points of the NMDS 2 dimmension

MDS = data.frame(pcoa1.16 = pcoa1.16, pcoa2.16 = pcoa2.16)
MDS = cbind(MDS, metadata)

set.seed(12345)
adonis2(transformed.16 ~ Location, metadata) # 0.026
adonis2(transformed.16 ~ plant, metadata)# 0.671
```
Time to make some plots, but first, I want to make a color scheme for all the future figures. Hopefully, it is color blind friendly 
```{r}
pal <- palette(c('#882255','#88CCEE','#EE8866', '#44AA99', '#117733', '#332288', '#DDCC77', '#999933','#CC6677',  '#AA4499', '#DDDDDD'))

# for small number of variables
largepal <- colorRampPalette(pal)(50) # for large number of variables
two.pal <- palette(c('#882255','#88CCEE'))
```

```{r, echo=FALSE}
ggplot(MDS, aes(x = pcoa1.16, y = pcoa2.16, color = treatment, shape = plant)) + geom_point(size =3) + scale_color_manual(values = pal) + theme_bw() + theme(text=element_text(size=20)) + labs(x = "PCOA1", y = "PCOA2") + geom_polygon(aes(group = treatment, fill = treatment), alpha = 0.5)+ scale_fill_manual(values = pal) + ylim(-0.7, 0.6) + xlim(-0.7, 0.6) + geom_label_repel(aes(label = SampleID), max.overlaps = 5, size = 3, label.padding = 0.1)
```

Is there a difference between the plants only in the buried treatments 

```{r}
S16merged <- transformed.16
S16merged <- as.data.frame(S16merged)
S16merged$SampleID <- c("NuBotR1", "NuBotR2", "NuBotR3", "NuTopR1", "NuTopR2", "NuTopR3", "NyBotR1", "NyBotR2", "NyBotR3", "NyTopR1", "NyTopR2", "NyTopR3")
S16merged$Location <- Location
S16merged$plant <- plant

S16buried <- S16merged %>% filter(Location == "buried")
S16buried <- S16buried[, colSums(S16buried != 0) > 0]

S16floating <- S16merged %>% filter(Location == "floating")
S16floating <- S16floating[, colSums(S16floating != 0) > 0]

set.seed(12345)
adonis2(S16buried[,c(1:3484)] ~ plant, S16buried) # 0.6
adonis2(S16floating[,c(1:1450)] ~ plant, S16floating) # 0.6

```

What is the difference between the communities for each treatment? What is the variability between the treatments and what causes this?

#### PCOA with ITS 

```{r, PCOA for ITS}
transformed.ITS <- t(ITS[,c(2:13)])
colnames(transformed.ITS) <- ASV.ITS
transformed.ITS[is.na(transformed.ITS)] <-0
transformed.ITS[c(1:630)] <- sapply(transformed.ITS[c(1:630)],as.numeric)

otu.bray.ITS <- vegdist(transformed.ITS, method = "bray")
pcoaVS.ITS <- ecodist::pco(otu.bray.ITS, negvals = "zero", dround = 0)

pcoa1.ITS = pcoaVS.ITS$vectors[,1] # adds the points of the NMDS 1 dimmension
pcoa2.ITS = pcoaVS.ITS$vectors[,2] # adds the points of the NMDS 2 dimmension

MDS = data.frame(pcoa1.ITS = pcoa1.ITS, pcoa2.ITS = pcoa2.ITS)
MDS = cbind(MDS, metadata)

set.seed(12345)
adonis2(transformed.ITS ~ Location, metadata) # 0.048
adonis2(transformed.ITS ~ plant, metadata)# 0.166
```

```{r, echo=FALSE}
ggplot(MDS, aes(x = pcoa1.ITS, y = pcoa2.ITS, color = treatment, shape = plant)) + geom_point(size =3) + scale_color_manual(values = pal) + theme_bw() + theme(text=element_text(size=20)) + labs(x = "PCOA1", y = "PCOA2") + geom_polygon(aes(group = treatment, fill = treatment), alpha = 0.5)+ scale_fill_manual(values = pal) + ylim(-0.7, 1.2) + xlim(-0.7, 1.2) + geom_label_repel(aes(label = SampleID), max.overlaps = 7, size = 3, label.padding = 0.1)
```
Is there a difference between the plants only in the buried treatments 

```{r}
ITSmerged <- transformed.ITS
ITSmerged <- as.data.frame(ITSmerged)
ITSmerged$SampleID <- c("NuBotR1", "NuBotR2", "NuBotR3", "NuTopR1", "NuTopR2", "NuTopR3", "NyBotR1", "NyBotR2", "NyBotR3", "NyTopR1", "NyTopR2", "NyTopR3")
ITSmerged$Location <- Location
ITSmerged$plant <- plant

ITSburied <- ITSmerged %>% filter(Location == "buried")
ITSburied <- ITSburied[, colSums(ITSburied != 0) > 0]

ITSfloating <- ITSmerged %>% filter(Location == "floating")
ITSfloating <- ITSfloating[, colSums(ITSfloating != 0) > 0]

set.seed(12345)
adonis2(ITSburied[,c(1:490)] ~ plant, ITSburied) # 0.4
adonis2(ITSfloating[,c(1:378)] ~ plant, ITSfloating) # 0.2

```

### PCOA with 18S eukaryotes 

```{r, PCOA for 18S}
transformed.18S.e <- t(S18.e[,c(2:13)])
colnames(transformed.18S.e) <- ASV.18.e
transformed.18S.e[is.na(transformed.18S.e)] <-0
transformed.18S.e[c(1:54)] <- sapply(transformed.18S.e[c(1:54)],as.numeric)

otu.bray.18S.e <- vegdist(transformed.18S.e, method = "bray")
pcoaVS.18S.e <- ecodist::pco(otu.bray.18S.e, negvals = "zero", dround = 0)

pcoa1.18s.e = pcoaVS.18S.e$vectors[,1] # adds the points of the NMDS 1 dimmension
pcoa2.18s.e = pcoaVS.18S.e$vectors[,2] # adds the points of the NMDS 2 dimmension

MDS = data.frame(pcoa1.18s.e = pcoa1.18s.e, pcoa2.18s.e = pcoa2.18s.e)
MDS = cbind(MDS, metadata)

set.seed(12345)
adonis2(transformed.18S.e ~ Location, metadata) # 0.042
adonis2(transformed.18S.e ~ plant, metadata)# 0.652
```
```{r, echo=FALSE}
ggplot(MDS, aes(x = pcoa1.18s.e, y = pcoa2.18s.e, color = treatment, shape = plant)) + geom_point(size =3) + scale_color_manual(values = pal) + theme_bw() + theme(text=element_text(size=20)) + labs(x = "PCOA1", y = "PCOA2") + geom_polygon(aes(group = treatment, fill = treatment), alpha = 0.5)+ scale_fill_manual(values = pal) + geom_label_repel(aes(label = SampleID), max.overlaps = 7, size = 3, label.padding = 0.1) + ylim(-0.8, 0.8) + xlim(-0.8, 0.8)
```
### PCOA with 18S eukaryotes 

```{r, PCOA for 18S}
transformed.18S.p <- t(S18.p[,c(2:13)])
colnames(transformed.18S.p) <- ASV.18.p
transformed.18S.p[is.na(transformed.18S.p)] <-0
transformed.18S.p[c(1:2231)] <- sapply(transformed.18S.p[c(1:2231)],as.numeric)

otu.bray.18S.p <- vegdist(transformed.18S.p, method = "bray")
pcoaVS.18S.p <- ecodist::pco(otu.bray.18S.p, negvals = "zero", dround = 0)

pcoa1.18s.p = pcoaVS.18S.p$vectors[,1] # adds the points of the NMDS 1 dimmension
pcoa2.18s.p = pcoaVS.18S.p$vectors[,2] # adds the points of the NMDS 2 dimmension

MDS = data.frame(pcoa1.18s.p = pcoa1.18s.p, pcoa2.18s.p = pcoa2.18s.p)
MDS = cbind(MDS, metadata)

set.seed(12345)
adonis2(transformed.18S.p ~ Location, metadata) # 0.023
adonis2(transformed.18S.p ~ plant, metadata)# 0.691
```
```{r, echo=FALSE}
ggplot(MDS, aes(x = pcoa1.18s.p, y = pcoa2.18s.p, color = treatment, shape = plant)) + geom_point(size =3) + scale_color_manual(values = pal) + theme_bw() + theme(text=element_text(size=20)) + labs(x = "PCOA1", y = "PCOA2") + geom_polygon(aes(group = treatment, fill = treatment), alpha = 0.5)+ scale_fill_manual(values = pal) + geom_label_repel(aes(label = SampleID), max.overlaps = 7, size = 3, label.padding = 0.1) + ylim(-0.8, 0.6) + xlim(-0.8, 0.6)
```
for all datasets, there is a difference between depths, but more variability in the bottom leaves, likely due to the influcence of the sediment on the leaves and the top leaves were bleached by the sun

## Phylum plots 

Look at the abundance of each phylum and make bar charts for the phyla within each kingdom 

For this, we have to make another table, I am calling it pivot here but it is a transposed table essentially 
```{r, 16S}
# remove ASVs that have no information 
pivot.16S <- S16 %>% filter(kingdom != "Unassigned", kingdom != "Alveolata") %>% pivot_longer(cols = c(NuBotR1:NyTopR3), names_to = "SampleID")

# if there are blanks, these should be NA
pivot.16S[pivot.16S == ""] <- NA   

pivot.16S <- pivot.16S %>% group_by(SampleID, kingdom, phylum, class, order, family, genus, species, ASV) %>% dplyr::summarize(value = sum(value))

phylum.16S <- pivot.16S %>% dplyr::select(SampleID, kingdom, phylum, value) %>% group_by(SampleID, kingdom, phylum) %>% dplyr::summarize(value = sum(value))

phylum.16S <- phylum.16S %>% pivot_wider(names_from = phylum, values_from = value)

phylum.16S[c(3:50)] <- sapply(phylum.16S[c(3:50)],as.numeric)
phylum.16S[is.na(phylum.16S)] <- 0

phylum.16S <- merge(metadata, phylum.16S, by = "SampleID")

# make a longer table, this is easier to graph with (hence why I named it ggplot)
phylum.ggplot.16S <- pivot_longer(phylum.16S, cols = p__Crenarchaeota:`NA`,names_to = "phylum", values_to = "value")

```

```{r}
ggplot(
    phylum.ggplot.16S %>% filter(value > 0),
    aes(fill = phylum, y = value, x = Location)
  ) + geom_bar(position = "fill", stat = "identity") + theme(legend.position = "right") + labs(y = "Relative Abundance") + theme_bw() + scale_fill_manual(values = largepal) + theme(text=element_text(size=20), legend.position = "bottom", legend.direction = "horizontal", plot.margin=unit(c(0,7,0,5), 'cm'))
```


