---
title: "Water Lilies Floating and Buried 18S eukaryote"
author: "Brianne Palmer"
date: "2023-02-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/briannepalmer/Library/CloudStorage/OneDrive-Personal/LeafFossilization/Leaf Fossilization R/Experiment 7")
```
There are several packages required to perform these analyses and create the figures. There are probably easier ways to do some of this, but if the code works, why change it?
```{r, Load Libraries}
library(phyloseq)
library(plyr)
library(data.table)
library(tidyverse)
library(vegan)
library(ecodist)
library(patchwork)
library(RColorBrewer)
library(ape)
library(microbiome)
library(microbiomeMarker)
library(ampvis2)
library(ggpubr)
library(ggvenn)
library(indicspecies)
library(ggpattern)
library(rstatix)
library(ggrepel)
```

Load Data
```{r}
S18 <- fread("/Users/briannepalmer/Library/CloudStorage/OneDrive-Personal/LeafFossilization/Leaf Fossilization R/Experiment 7/data/Experiment7/experiment7_18S.csv")

S18[S18 == ""] <- NA   

```

```{r}
# the metadata 
metadata <- fread("/Users/briannepalmer/Library/CloudStorage/OneDrive-Personal/LeafFossilization/Leaf Fossilization R/Experiment 7/data/Experiment7/experiment7_metadata.csv")

metadata <- metadata %>% filter(Plant != "None")
```

```{r}
# make new columns with count and relative abundance 
S18[,c(2:13)] <-sweep(S18[,c(2:13)], 2, colSums(S18[,c(2:13)]), `/`)
S18$n <- rowSums(S18[ , c(2:13)], na.rm=TRUE)

S18.e <- S18 %>% filter(kingdom %in% c("Eukaryota", "Eukaryota:mito", "Eukaryota:plas"))
ASV.18.e <- as.vector(paste0("ASV", seq(1:54)))
S18.e$ASV <- ASV.18.e
```

Make another table with the ASVs as columns, this is necessary for the PCOA

```{r, PCOA for 16S}
library(funrar)

transformed.18S <- t(S18.e[,c(2:13)])
colnames(transformed.18S) <- ASV.18.e
transformed.18S[is.na(transformed.18S)] <-0
transformed.18S[c(1:54)] <- sapply(transformed.18S[c(1:54)],as.numeric)

ITS.rel <- make_relative(transformed.18S)

otu.bray.18S <- vegdist(ITS.rel, method = "bray")
pcoaVS.18S <- ecodist::pco(otu.bray.18S, negvals = "zero", dround = 0)

pcoa1.18S = pcoaVS.18S$vectors[,1] # adds the points of the NMDS 1 dimmension
pcoa2.18S = pcoaVS.18S$vectors[,2] # adds the points of the NMDS 2 dimmension

MDS = data.frame(pcoa1.18S = pcoa1.18S, pcoa2.18S = pcoa2.18S)
MDS = cbind(MDS, metadata)

set.seed(12345)
adonis2(transformed.18S ~ Treatment, metadata) 
adonis2(transformed.18S ~ Location, metadata)
adonis2(transformed.18S ~ Plant, metadata)
```
Time to make some plots, but first, I want to make a color scheme for all the future figures. Hopefully, it is color blind friendly 
```{r}
pal <- palette(c('#882255','#88CCEE','#EE8866','#44AA99','#117733','#332288','#DDCC77','#999933','#CC6677','#AA4499','#DDDDDD'))
largepal <- colorRampPalette(pal)(50) # for large number of variables
two.pal <- palette(c('#882255','#88CCEE'))
```

```{r}
pcoa <- ggplot(data = MDS, aes(x = pcoa1.18S, y = pcoa2.18S, shape = Treatment)) + geom_point(size =3, color = '#44AA99') + theme_bw() + theme(text=element_text(size=20)) +labs(x = "PCOA1", y = "PCOA2")
pcoa

pdf("figures/Experiment7/NymphaeaNuphar_Figures_April2023/pcoa_18S.pdf")
pcoa
dev.off()
```


```{r, echo=FALSE}
pdf("figures/WaterLilyTopBottom_PCOA_18S.pdf", height = 12, width = 12)
ggplot(MDS, aes(x = pcoa1.18S, y = pcoa2.18S, color = treatment, shape = plant)) + geom_point(size =3) + scale_color_manual(values = pal) + theme_bw() + theme(text=element_text(size=20)) + labs(x = "PCOA1", y = "PCOA2") + geom_polygon(aes(group = treatment, fill = treatment), alpha = 0.5)+ scale_fill_manual(values = pal) + geom_label_repel(aes(label = SampleID), max.overlaps = 10, size = 3, label.padding = 0.1) + ylim(-0.8, 0.8) + xlim(-0.8, 0.8)
dev.off()
```


Look at the abundance of each phylum and make bar charts for the phyla within each kingdom 

For this, we have to make another table, I am calling it pivot here but it is a transposed table essentially 
```{r, 16S}
# remove ASVs that have no information 
pivot.18S <- S18.e %>% filter(kingdom != "Unassigned", kingdom != "Alveolata") %>% pivot_longer(cols = c(NuBotR1:NyTopR3), names_to = "SampleID")

# if there are blanks, these should be NA
pivot.18S[pivot.18S == ""] <- NA   

pivot.18S <- pivot.18S %>% group_by(SampleID, kingdom, phylum, class, order, family, genus, species, ASV) %>% dplyr::summarize(value = sum(value))

phylum.18S <- pivot.18S %>% dplyr::select(SampleID, kingdom, phylum, value) %>% group_by(SampleID, kingdom, phylum) %>% dplyr::summarize(value = sum(value))

phylum.18S <- phylum.18S %>% pivot_wider(names_from = phylum, values_from = value)

phylum.18S[c(3:10)] <- sapply(phylum.18S[c(3:10)],as.numeric)
phylum.18S[is.na(phylum.18S)] <- 0

phylum.18S <- merge(metadata, phylum.18S, by = "SampleID")

# make a longer table, this is easier to graph with (hence why I named it ggplot)
phylum.ggplot.18S <- pivot_longer(phylum.18S, cols = Fungi:`Streptophyta:plas`,names_to = "phylum", values_to = "value")

```

```{r}
pdf("figures/Experiment7/NymphaeaNuphar_Figures_April2023/phylum_barchart_18S.pdf", height = 12, width = 18)
ggplot(
    phylum.ggplot.18S %>% filter(value > 0, phylum != "NA"),
    aes(fill = phylum, y = value, x = Treatment)
  ) + geom_bar(position = "fill", stat = "identity") + theme(legend.position = "right") + labs(y = "Relative Abundance") + theme_bw() + theme(text=element_text(size=20), legend.position = "right", legend.direction = "vertical", axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + scale_fill_manual(values = pal)
dev.off()
```

```{r}
phylum.anova <- phylum.ggplot.18S %>% group_by(phylum) %>%
  do(broom::tidy(TukeyHSD(aov(value ~ Location, data = .)))) %>%
  ungroup

phylum.anova.sig <- phylum.anova %>% filter(adj.p.value < 0.05) 

phylum.anova.sig
```

```{r}
S182 <- fread("/Users/briannepalmer/Library/CloudStorage/OneDrive-Personal/LeafFossilization/Leaf Fossilization R/Experiment 7/data/Experiment7/experiment7_18S.csv")
S182[S182 == ""] <- NA 
S18.e2 <- S182 %>% filter(kingdom %in% c("Eukaryota", "Eukaryota:mito", "Eukaryota:plas"))

S18.e2$ASV <- ASV.18.e

otu.table <- S18.e2[,c(2:13)]
otu.table <- as.matrix(otu.table)
rownames(otu.table) <- S18.e2$ASV
tax.table <- S18.e2[,c(14:21)]
tax.table <- as.matrix(tax.table)
rownames(tax.table) <- S18.e2$ASV

otu.table <- otu_table(otu.table, taxa_are_rows = TRUE)
tax.table <- tax_table(tax.table)
sam.data <- as.matrix(metadata)
sam.data <- sample_data(metadata)
rownames(sam.data) <- metadata$SampleID

ps <- phyloseq(otu.table, tax.table, sam.data)
random_tree = rtree(ntaxa(ps), rooted=TRUE, tip.label=taxa_names(ps))

ps = merge_phyloseq(ps,random_tree)
ps <- subset_taxa(ps, kingdom !="Unassigned")
ps <- subset_taxa(ps, phylum != "NA")

p = plot_richness(ps, x="Treatment", color ="Treatment", measures=c("Observed","Shannon", "Simpson")) + geom_point() + theme_bw() + geom_boxplot() + scale_color_manual(values = pal) + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), legend.position = "none") 


pdf("figures/Experiment7/NymphaeaNuphar_Figures_April2023/diversityplot_18S.pdf")
p
dev.off()
```


But diversity and richness may vary by treatment or even between sample IDs

Make a new dataframe with the ASVs from the pivot dataframe
```{r}
ASV <- pivot.18S %>% dplyr::select(SampleID, ASV, value) # the pivot dataframe also removed all the ASVs that were unassigned at the kingdom level 
ASV <- ASV %>% pivot_wider(names_from = ASV, values_from = value)
ASV[c(9:62)] <- sapply(ASV[c(9:62)],as.numeric)
ASV[c(9:62)][is.na(ASV[c(9:62)])] <- 0
ASV <- merge(metadata, ASV)
ASV.gp <- ASV %>% group_by(SampleID, Location, Plant, Treatment) %>% summarize_at(vars(ASV35:ASV28), sum)

```

```{r}
ASV.long <- pivot_longer(ASV.gp, cols = ASV35:ASV28, names_to = "ASV", values_to = "count")

y <- ASV.long %>% dplyr::select(Treatment, ASV, count)

NuBot = y %>% filter(Treatment == "NupharBuried")  %>% filter(count >0) %>% dplyr::select(ASV) #48
NuTop = y %>% filter(Treatment == "NupharFloating")  %>% filter(count >0) %>% dplyr::select(ASV) #19
NyBot = y %>% filter(Treatment == "NymphaeaBuried")  %>% filter(count >0) %>% dplyr::select(ASV) #39
NyTop = y %>% filter(Treatment == "NymphaeaFloating")  %>% filter(count >0) %>% dplyr::select(ASV) #26


y <- rbind(NuBot, NuTop, NyBot, NyTop)

Treatment <- c(rep("NupharBuried", 48), rep("NupharFloating", 19), rep("NymphaeaBuried", 39), rep("NymphaeaFloating", 26))

y$Treatment <- Treatment

x <- list(NupharBuried = y$ASV[1:48], NupharFloating = y$ASV[49:67], NymphaeaBuried = y$ASV[68:106], NymphaeaFloating = y$ASV[107:132])
```

```{r, echo=FALSE}
venn <- ggvenn(
  x, 
  fill_color = pal,
  stroke_size = 0.5, set_name_size = 3.5, show_percentage = TRUE) 

pdf("figures/Experiment7/NymphaeaNuphar_Figures_April2023/venn_18s.pdf")
venn
dev.off()
```

```{r}
otu.table <- as.data.frame(ps@otu_table)
tax.table <- as.data.frame(ps@tax_table)

d <- amp_load(otutable = otu.table,
              metadata = metadata,
              taxonomy = tax.table)

amp_rank_abundance(d, "Location", showSD = TRUE, log10_x = TRUE)

amp_rarecurve(
  d,
  stepsize = 1000,
  color_by = "SampleID",
  facet_by = NULL,
  facet_scales = "fixed"
) # cool cool, the rarfaction curve sucks for the eukaryotes

amp_octave(
  d,
  tax_aggregate = "OTU",
  group_by = 1L,
  scales = "fixed",
  num_threads = parallel::detectCores() - 2L
)

d.rare <-amp_rarefy(d, 67)

pdf("figures/WaterLiliesTopBottom_Heatmap18S.pdf", width = 14, height = 20)
amp_heatmap(data = d.rare, 
             tax_aggregate = "Genus",
             tax_add = "Phylum",
             group_by = c("SampleID"),
             tax_show = 25,
             plot_colorscale = "log10",
            facet_by = "Treatment",
            color_vector = NULL)
dev.off()

tax_vector <- c("g__uncultured", "NA", "")
d.known.genera <- amp_filter_taxa(d.rare, 
                                  tax_vector = tax_vector, 
                                  remove = TRUE)

genus.heatmap <- amp_heatmap(data = d.known.genera, 
             tax_aggregate = "Genus",
             tax_add = "Phylum",
             group_by = c("Treatment"),
             tax_show = 10,
             plot_colorscale = "log10",
             plot_values = FALSE)


pdf("figures/Experiment7/NymphaeaNuphar_Figures_April2023/heatmap_18S.pdf")
genus.heatmap
dev.off()
```

```{r}
alpha <- amp_alpha_diversity(d.rare)

rich.lm <- lm(ObservedOTUs ~ Plant, data = alpha)
rich.aov <- aov(rich.lm)
summary(rich.aov)

div.lm <- lm(Shannon ~ Location, data = alpha)
div.aov <- aov(div.lm)
summary(div.aov)

div.lm <- lm(Simpson ~ Plant, data = alpha)
div.aov <- aov(div.lm)
summary(div.aov)

div.lm <- lm(invSimpson ~ Plant, data = alpha)
div.aov <- aov(div.lm)
summary(div.aov)


amp_otu_network(
  d,
  min_abundance = 0,
  color_by = "treatment",
  tax_aggregate = "Phylum",
  tax_add = NULL,
  tax_show = 10,
  tax_class = NULL,
  tax_empty = "best",
  normalise = TRUE
)


amp_venn(
  d.rare,
  group_by = "Location",
  cut_a = 0.1,
  cut_f = 80,
  text_size = 5,
  normalise = TRUE,
  detailed_output = FALSE
)

```

Look at richness and diversity between all samples
```{r}
ggplot(data = alpha, aes(x = SampleID, y = ObservedOTUs, color = Location, shape = plant)) + geom_point(size = 5) + theme_bw() + theme(legend.position = "none")  + labs(y = "# of ASV", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_color_manual(values = two.pal) + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1)) 
```


```{r}
ggplot(data = alpha, aes(x = treatment, y = ObservedOTUs, fill = Location)) + geom_violin() + theme_bw() + theme(legend.position = "none")  + labs(y = "# of ASV", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_fill_manual(values = two.pal) + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1)) +
  geom_violin_pattern(pattern = 'circle',
                    color = "gray", 
                   pattern_fill = "gray",
                   pattern_angle = 45,
                   pattern_density = 0.1,
                   pattern_spacing = 0.025,
                   pattern_key_scale_factor = 0.6)
```

```{r}
nubot.rich.plot <- ggplot(data = alpha %>% filter(treatment == "NuBot"), aes(x = SampleID, y = ObservedOTUs, color = Location, shape = plant)) + geom_point(size = 5) + theme_bw() + labs(y = "# of ASV", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_color_manual(values = '#882255') + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1)) + ylim(0,16)+ theme(legend.position = "none") 

nutop.rich.plot <- ggplot(data = alpha %>% filter(treatment == "NuTop"), aes(x = SampleID, y = ObservedOTUs, color = Location, shape = plant)) + geom_point(size = 5) + theme_bw()+ labs(y = "# of ASV", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_color_manual(values = '#88CCEE') + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1)) + ylim(0,16)+ theme(legend.position = "none") 

nybot.rich.plot <- ggplot(data = alpha %>% filter(treatment == "NyBot"), aes(x = SampleID, y = ObservedOTUs, color = Location, shape = plant)) + geom_point(size = 5) + theme_bw() + labs(y = "# of ASV", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_color_manual(values = '#EE8866') + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1)) + ylim(0,16)+ theme(legend.position = "none") 

nytop.rich.plot <- ggplot(data = alpha %>% filter(treatment == "NyTop"), aes(x = SampleID, y = ObservedOTUs, color = Location, shape = plant)) + geom_point(size = 5) + theme_bw() + labs(y = "# of ASV", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_color_manual(values = '#44AA99') + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1)) + ylim(0,16)+ theme(legend.position = "none") 

pdf("figures/WaterLiliesTopBottom_Richness_18S.pdf", width = 14)
nubot.rich.plot + nutop.rich.plot + nybot.rich.plot + nytop.rich.plot + plot_layout(ncol = 4, nrow = 1)
dev.off()
```

```{r}
ggplot(data = alpha, aes(x = Location, y = ObservedOTUs, fill = Location)) + geom_violin() + theme_bw() + theme(legend.position = "none")  + labs(y = "# of ASV", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_fill_manual(values = two.pal) + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1))  

ggplot(data = alpha, aes(x = Location, y = Shannon, fill = Location)) + geom_violin() + theme_bw() + theme(legend.position = "none")  + labs(y = "Shannon Diversity", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_fill_manual(values = two.pal) + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1))  
```
```{r}
nubot.div.plot <- ggplot(data = alpha %>% filter(treatment == "NuBot"), aes(x = SampleID, y = Shannon, color = Location, shape = plant)) + geom_point(size = 5) + theme_bw() + labs(y = "Shannon Diversity", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_color_manual(values = '#882255') + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1)) + theme(legend.position = "none") + ylim(0, 2)

nutop.div.plot <- ggplot(data = alpha %>% filter(treatment == "NuTop"), aes(x = SampleID, y = Shannon, color = Location, shape = plant)) + geom_point(size = 5) + theme_bw()+ labs(y = "Shannon Diversity", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_color_manual(values = '#88CCEE') + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1)) + theme(legend.position = "none") + ylim(0,2)

nybot.div.plot <- ggplot(data = alpha %>% filter(treatment == "NyBot"), aes(x = SampleID, y = Shannon, color = Location, shape = plant)) + geom_point(size = 5) + theme_bw() + labs(y = "Shannon Diversity", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_color_manual(values = '#EE8866') + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1)) + theme(legend.position = "none") + ylim(0,2)

nytop.div.plot <- ggplot(data = alpha %>% filter(treatment == "NyTop"), aes(x = SampleID, y = Shannon, color = Location, shape = plant)) + geom_point(size = 5) + theme_bw() + labs(y = "Shannon Diversity", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_color_manual(values = '#44AA99') + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1)) + theme(legend.position = "none") + ylim(0,2)

pdf("figures/WaterLiliesTopBottom_ShannonDiversity_18S.pdf", width = 14)
nubot.div.plot + nutop.div.plot + nybot.div.plot + nytop.div.plot + plot_layout(ncol = 4, nrow = 1)
dev.off()
```

```{r}

ggplot(data = alpha, aes(x = SampleID, y = Shannon, color = Location, shape = plant)) + geom_point(size = 5) + theme_bw() + theme(legend.position = "none")  + labs(y = "Shannon Diversity", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_color_manual(values = two.pal) + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1)) 

ggplot(data = alpha, aes(x = treatment, y = Shannon, fill = Location)) + geom_violin() + theme_bw() + theme(legend.position = "none")  + labs(y = "Shannon Diversity", x = "Location") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) + theme_bw() + scale_fill_manual(values = two.pal) + theme(text=element_text(size=20)) + theme (axis.text.x = element_text (angle = 45, vjust = 1, hjust=1)) 
```


DESEQ
```{r}
ps1 <- subset_samples(ps, Plant != "None")
wh0 = genefilter_sample(ps1, filterfun_sample(function(x) x > 5), A=0.5*nsamples(ps1)) # removes low abundance pathways
GP1 = prune_taxa(wh0, ps1)
GP1 = transform_sample_counts(GP1, function(x) 1E6 * x/sum(x))
mb <- GP1
library(DESeq2)

#install.packages("C:/Users/Brianne/Downloads/locfit_1.5-9.tar.gz", repos = NULL, type="source")

# First, we will convert the sequence count data from our phyloseq object into the proper format for DESeq2
mb.dds <- phyloseq_to_deseq2(mb, ~ Location)

# Next we need to estimate the size factors for our sequences
gm_mean = function(x, na.rm=TRUE){
    exp(sum(log(x[x > 0]), na.rm=na.rm) / length(x))
}
geoMeans = apply(counts(mb.dds), 1, gm_mean)
mb.dds = estimateSizeFactors(mb.dds, geoMeans = geoMeans)

# Finally, we can run the core DESeq2 algorithm
mb.dds = DESeq(mb.dds, fitType="local")

# Create a new dataframe from the results of our DESeq2 run
mb.res = results(mb.dds)

# Reorder the sequences by their adjusted p-values
mb.res = mb.res[order(mb.res$padj, na.last=NA), ]

# Set your alpha for testing significance, and filter out non-significant results
alpha = 0.05
mb.sigtab = mb.res[(mb.res$padj < alpha), ]

mb.res = cbind(as(mb.res, "data.frame"), as(tax_table(mb)[rownames(mb.res), ], "matrix"))

# Add taxonomy information to each sequence
# mb.sigtab = cbind(as(mb.sigtab, "data.frame"), as(tax_table(mb)[rownames(mb.sigtab), ], "matrix"))
# head(mb.sigtab)
# 
# mb.sigtab$group<- ifelse(mb.sigtab$log2FoldChange < 0, 'buried','floating')
# mb.sigtab$color <- ifelse(mb.sigtab$log2FoldChange < 0, '#882255','#88CCEE')
# mb.ns <- mb.res %>% filter(padj > 0.05)
# 
# volcano.plot <- ggplot(mb.sigtab, aes(x = log2FoldChange, y = -log10(padj))) + geom_point(color = mb.sigtab$color, size = 4) + geom_hline(aes(yintercept =-log10(0.05)), linetype = "dashed") + theme_bw() + geom_point(data = mb.ns, mapping = aes(x = mb.ns$log2FoldChange, y = -log10(mb.ns$padj)), color = "gray", size = 4) + ggrepel::geom_label_repel(aes(label = rownames(mb.sigtab)), max.overlaps = 20, size = 5, label.padding = 0.1) + theme(text=element_text(size=20)) 
# 
# volcano.plot

```
