---
---
title: "Experiment 7 Bacterial Community"
author: "Brianne"
date: '2022-07-22'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/briannepalmer/Library/CloudStorage/OneDrive-Personal/Leaf Fossilization Experiment 7/Experiment 7")
```

required Libraries 
```{r}
library(tidyverse)
```

```{r}
pal <- palette(c("#0073C2FF", "#EFC000FF" , "#f08080", "#CD534CFF"))
pal <- colorRampPalette(pal)(25)
```


Load bacteria OTU data and create a new column for relative abundance, use relative abundance values throughout

```{r}
diatoms <- fread("waterlilies_.txt")
diatoms <- diatoms %>% dplyr::rename(OTU = V2)
diatoms <- diatoms %>%  add_count(OTU)  %>% filter(kingdom != "k__metazoa") %>% filter(order != "o__nymphaeales")
diatoms.gp <- diatoms %>% group_by(SampleID, OTU) %>% summarize(n = sum(n))
diatoms.gp <- diatoms.gp %>% mutate(rel = n / sum(n))
```
Load metadata file
```{r}
SampleID <- unique(diatoms$SampleID)
plant <- c("nuphar", "nuphar", "nuphar", "nuphar", "nuphar", "nuphar", "nymphaea", "nymphaea", "nymphaea", "nymphaea", "nymphaea", "nymphaea")
Location <- c("Bottom", "Bottom", "Bottom", "Top", "Top", "Top", "Bottom", "Bottom", "Bottom", "Top", "Top", "Top")
Replicate <- c("R1", "R2", "R3","R1", "R2", "R3","R1", "R2", "R3","R1", "R2", "R3")
Treatment <-c("nuphar_bottom", "nuphar_bottom", "nuphar_bottom", "nuphar_top", "nuphar_top", "nuphar_top", "nymphaea_bottom", "nymphaea_bottom", "nymphaea_bottom", "nymphaea_top", "nymphaea_top", "nymphaea_top")

metadata <- data.frame(SampleID, Treatment, plant, Replicate, Location)

```

Transpose the 'bacteria' file so the OTUs are columns, make all OTU values numeric and make NAs = 0. Then group by SampleID to get 30 lines and create a new file with the OTU values only 
```{r}
diatoms.t <- diatoms.gp %>% pivot_wider(names_from =OTU, values_from = rel)
diatoms.t[c(3:462)] <- sapply(diatoms.t[c(3:462)],as.numeric)
diatoms.t[c(3:462)][is.na(diatoms.t[c(3:462)])] <-0
diatoms.t <- diatoms.t %>% group_by(SampleID) %>% summarize_all(sum)
otu.only <- diatoms.t[3:462]
```

```{r}
phylum <-  diatoms %>% group_by(SampleID, kingdom, phylum) %>% summarize(n = sum(n))%>% mutate(rel = n / sum(n))
phylum <- phylum %>% dplyr::select(SampleID, kingdom, phylum, rel)
phylum <- phylum %>% pivot_wider(names_from = phylum, values_from = rel)
phylum[c(3:30)] <- sapply(phylum[c(3:30)],as.numeric)
phylum[is.na(phylum)] <- 0

phylum <- as.data.frame(c(metadata, phylum))
phylum.ggplot <- pivot_longer(phylum, cols = p__apicomplexa:p__entomophthoromycota,names_to = "phylum", values_to = "count")
```


```{r, tidy=TRUE, tidy.opts=list(width.cutoff=50)}
ggplot(phylum.ggplot, aes(fill = phylum, y = count, x = Treatment)) + geom_bar(position = "fill", stat = "identity")  + theme(axis.text.x = element_text(size = 10)) + theme(legend.position = "right") + labs(y = "Relative Abundance")  +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = .5,
    hjust = 1
  )) + facet_grid(. ~ kingdom)

```

Which phyla vary by Treatment

```{r}
phylum.anova <- phylum.ggplot %>% group_by(phylum) %>%
  do(broom::tidy(TukeyHSD(aov(count ~ Treatment, data = .)))) %>%
  ungroup

phylum.anova.treatment <- phylum.anova %>% filter(adj.p.value < 0.05)
```

```{r}
diatoms.all <- as.data.frame(c(metadata, diatoms.t))
diatoms.all$Treatment <- as.factor(diatoms.all$Treatment)
```


```{r}
library(vegan)
claytop.rich <- specnumber((bacteria.all %>% filter(Treatment == "clay_top"))[-c(1:7)])
claybot.rich <- specnumber((bacteria.all %>% filter(Treatment == "clay_bottom" ))[-c(1:7)])
controltop.rich <- specnumber((bacteria.all %>% filter(Treatment == "control_top" ))[-c(1:7)])
controlbot.rich <- specnumber((bacteria.all %>% filter(Treatment == "control_bottom" ))[-c(1:7)])
glrich <- specnumber((bacteria.all %>% filter(Treatment == "greenleaf" ))[-c(1:7)])
monttop.rich <- specnumber((bacteria.all %>% filter(Treatment == "montmorillonite_top" ))[-c(1:7)])
montbot.rich <- specnumber((bacteria.all %>% filter(Treatment == "montmorillonite_bottom" ))[-c(1:7)])
pondtop.rich <- specnumber((bacteria.all %>% filter(Treatment == "pond_top" ))[-c(1:7)])
pondlbot.rich <- specnumber((bacteria.all %>% filter(Treatment == "pond_bottom" ))[-c(1:7)])
sandtop.rich <- specnumber((bacteria.all %>% filter(Treatment == "sand_top" ))[-c(1:7)])
sandbot.rich <- specnumber((bacteria.all %>% filter(Treatment == "sand_bottom" ))[-c(1:7)])
```

```{r}
claytop.div <- vegan::diversity((bacteria.all %>% filter(Treatment == "clay_top"))[-c(1:7)])
claybot.div <- vegan::diversity((bacteria.all %>% filter(Treatment == "clay_bottom" ))[-c(1:7)])
controltop.div <- vegan::diversity((bacteria.all %>% filter(Treatment == "control_top" ))[-c(1:7)])
controlbot.div <- vegan::diversity((bacteria.all %>% filter(Treatment == "control_bottom" ))[-c(1:7)])
gldiv <- vegan::diversity((bacteria.all %>% filter(Treatment == "greenleaf" ))[-c(1:7)])
monttop.div <- vegan::diversity((bacteria.all %>% filter(Treatment == "montmorillonite_top" ))[-c(1:7)])
montbot.div <- vegan::diversity((bacteria.all %>% filter(Treatment == "montmorillonite_bottom" ))[-c(1:7)])
pondtop.div <- vegan::diversity((bacteria.all %>% filter(Treatment == "pond_top" ))[-c(1:7)])
pondlbot.div <- vegan::diversity((bacteria.all %>% filter(Treatment == "pond_bottom" ))[-c(1:7)])
sandtop.div <- vegan::diversity((bacteria.all %>% filter(Treatment == "sand_top" ))[-c(1:7)])
sandbot.div <- vegan::diversity((bacteria.all %>% filter(Treatment == "sand_bottom" ))[-c(1:7)])
```


```{r}
richness <- c(claytop.rich,claybot.rich,controltop.rich,controlbot.rich, glrich,monttop.rich, montbot.rich, pondtop.rich,pondlbot.rich,sandtop.rich, sandbot.rich)
diversity <- c(claytop.div,claybot.div,controltop.div,controlbot.div, gldiv,monttop.div, montbot.div, pondtop.div,pondlbot.div,sandtop.div, sandbot.div)
```

```{r}
# make new data frame 

rich.div <- data.frame(bacteria.all$Treatment, bacteria.all$Substrate, bacteria.all$Location, richness, diversity)
```

```{R}
rich.lm <- lm(richness ~ bacteria.all.Substrate, data = rich.div)
rich.aov <- aov(rich.lm)
summary(rich.aov)# there is a difference in OTU richness 

TukeyHSD(rich.aov)
```

```{r}
div.lm <- lm(diversity ~ bacteria.all.Substrate, data = rich.div)
div.aov <- aov(div.lm)
summary(div.aov)# there is a difference in OTU diversity 
TukeyHSD(div.aov)
```

```{r}

richness.plot <- ggplot(data = rich.div, aes(x = bacteria.all.Treatment, y = richness, fill = bacteria.all.Treatment)) + geom_boxplot() + theme_bw() + theme(legend.position = "none") + theme(text=element_text(size=20)) + labs(y = "# of OTUs", x = "Treatment") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
richness.plot

diversiy.plot <- ggplot(data = rich.div, aes(x = bacteria.all.Treatment, y = diversity, fill = bacteria.all.Location)) + geom_boxplot()+ theme(legend.position = "none") + theme(text=element_text(size=20)) + labs(y = "Shannon-Weiner Diversity", x = "Treatment") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

diversiy.plot

```

```{r}
genus <- diatoms %>% group_by(SampleID, kingdom, genus) %>% summarize(n = sum(n))%>% mutate(rel = n / sum(n))
genus <- genus %>% dplyr::select(SampleID, genus, rel)
genus[is.na(genus)] <- NA
genus <- genus %>% pivot_wider(names_from = genus, values_from = rel)
genus[c(2:211)] <- sapply(genus[c(2:211)],as.numeric)
genus[is.na(genus)] <- 0

genus <- as.data.frame(c(metadata, genus))
genus.ggplot <- genus %>% group_by(Treatment, Location, plant, kingdom) %>% summarize_at(vars(g__acremonium:g__sclerotinia), mean)

genus.ggplot <- pivot_longer(genus, cols = g__acremonium:g__sclerotinia, names_to = "genus", values_to = "count")

genus.ggplot <- genus.ggplot %>% group_by(Treatment, genus, Location, plant, kingdom) %>% summarize(mean = mean(count))
```

```{r}
ggplot(genus.ggplot %>% filter(kingdom == "k__eukaryota") , aes(fill = genus, y = mean, x = Treatment)) + geom_bar(position = "dodge", stat = "identity") + theme_bw() + theme(axis.text.x = element_text(size = 10)) + theme(legend.position = "right") + labs(y = "Relative Abundance")  +
  theme(axis.text.x = element_text(
    angle = 90,
    vjust = .5,
    hjust = 1
  )) 

```


```{r}
genus.anova <- genus.ggplot %>% group_by(genus) %>%
  do(broom::tidy(TukeyHSD(aov(mean ~ plant, data = .)))) %>%
  ungroup

genus.anova.treatment <- genus.anova %>% filter(adj.p.value < 0.05)

```
