---
title: "NymphaeaNuphar_ITS_April2023_update"
author: "Brianne Palmer"
date: "2023-04-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir ="/Users/briannepalmer/Library/CloudStorage/OneDrive-Personal/LeafFossilization/Leaf Fossilization R/Experiment 7")
```

This document contains all the code for Experiment 7 -- Nymphaea Nuphar Buried and Floating. The primary file used here contains the ITS sequences for the water lily leaves and for the soil and water. 

```{r, Load Libraries}
library(phyloseq)
library(plyr)
library(data.table)
library(tidyverse)
library(vegan)
library(ecodist)
library(RColorBrewer)
library(ape)
library(ampvis2)
library(ggpubr)
library(ggvenn)
library(ggpattern)
library(rstatix)
library(ggrepel)
library(funrar)
library(DESeq2)
```

```{r, Load Data}
ITS <- fread("/Users/briannepalmer/Library/CloudStorage/OneDrive-Personal/LeafFossilization/Leaf Fossilization R/Experiment 7/data/Experiment7/waterlilies_w_soilwaterITS.csv")
```

```{r, metadata}
metadata <- fread("/Users/briannepalmer/Library/CloudStorage/OneDrive-Personal/LeafFossilization/Leaf Fossilization R/Experiment 7/data/Experiment7/experiment7_metadata.csv")
xITS <- seq(1:1288)
```

```{r}
ASV.ITS <- as.vector(paste0("ASV", xITS))
ITS$ASV <- ASV.ITS

ITS[,c(9:26)][is.na(ITS[,c(9:26)])] <- 0
```

```{r, PCOA}
transformed.ITS <- t(ITS[,c(9:26)])

colnames(transformed.ITS) <- ASV.ITS
transformed.ITS[is.na(transformed.ITS)] <-0
transformed.ITS[c(1:1288)] <- sapply(transformed.ITS[c(1:1288)],as.numeric)

ITS.rel <- make_relative(transformed.ITS)

otu.bray.ITS <- vegdist(ITS.rel, method = "bray")
pcoaVS.ITS <- ecodist::pco(otu.bray.ITS, negvals = "zero", dround = 0)

pcoa1.ITS = pcoaVS.ITS$vectors[,1] # adds the points of the NMDS 1 dimmension
pcoa2.ITS = pcoaVS.ITS$vectors[,2] # adds the points of the NMDS 2 dimmension

MDS = data.frame(pcoa1.ITS = pcoa1.ITS, pcoa2.ITS = pcoa2.ITS)
MDS = cbind(MDS, metadata)
```

```{r}
set.seed(12345)
adonis2(transformed.ITS ~ Treatment, metadata) 
adonis2(transformed.ITS ~ Location, metadata)
```


```{r}
pcoa <- ggplot(data = MDS, aes(x = pcoa1.ITS, y = pcoa2.ITS, color = Treatment)) + geom_point(size =6, alpha = 0.5) + theme_bw() + theme(text=element_text(size=20),legend.title=element_blank(), legend.position = "bottom") +labs(x = "PCOA1", y = "PCOA2") + ggtitle("B.") + xlim(-0.2, 0.4) + ylim(-0.2, 0.4) + scale_color_manual(values = c('#88CCEE','#882255', '#44AA99','#EE8866','#DDCC77','#332288'))

pcoa


png("figures/Experiment7/June_Revision_Figures /ITS_forposter.png", width = 15, height = 20, units = 'cm', res = 300)
ggplot(data = MDS, aes(x = pcoa1.ITS, y = pcoa2.ITS, color = Treatment)) + geom_point(size =8, alpha = 0.5) + theme_bw() + theme(text=element_text(size=20),legend.title=element_blank(), legend.position = "right") +labs(x = "PCOA1", y = "PCOA2") + xlim(-0.2, 0.4) + ylim(-0.2, 0.4) + scale_color_manual(values = c('#88CCEE','#882255', '#44AA99','#EE8866','#DDCC77','#332288'))
dev.off()
```

```{r}
transformed.ITS.leaves <- transformed.ITS[-c(1:6),]

ITS.rel.leaves <- make_relative(transformed.ITS.leaves)

otu.bray.ITS <- vegdist(ITS.rel.leaves, method = "bray")
pcoaVS.ITS <- ecodist::pco(otu.bray.ITS, negvals = "zero", dround = 0)

pcoa1.ITS = pcoaVS.ITS$vectors[,1] # adds the points of the NMDS 1 dimmension
pcoa2.ITS = pcoaVS.ITS$vectors[,2] # adds the points of the NMDS 2 dimmension

metadata.leaves <- metadata %>% filter(Plant != "None")
MDS = data.frame(pcoa1.ITS = pcoa1.ITS, pcoa2.ITS = pcoa2.ITS)
MDS = cbind(MDS, metadata.leaves)
```

```{r}
set.seed(12345)
adonis2(transformed.ITS.leaves ~ Treatment, metadata.leaves) 
adonis2(transformed.ITS.leaves ~ Location, metadata.leaves)
adonis2(transformed.ITS.leaves ~ Plant, metadata.leaves)
```

```{r}
pal <- palette(c('#882255', '#88CCEE', '#EE8866', '#44AA99', '#117733', '#332288', '#DDCC77', '#999933', '#CC6677', '#AA4499', '#DDDDDD'))
```

```{r}
ggplot(data = MDS, aes(x = pcoa1.ITS, y = pcoa2.ITS, shape = Treatment)) + geom_point(size =3) + theme_bw() + theme(text=element_text(size=20)) +labs(x = "PCOA1", y = "PCOA2") 
```

RELATIVE ABUNDANCE OF PHYLA

```{r}
# remove ASVs that have no information 
pivot.ITS <- ITS %>% filter(kingdom != "Unassigned", kingdom != "Alveolata") %>% pivot_longer(cols = c(BS1:NyTopR3), names_to = "SampleID")

# if there are blanks, these should be NA
pivot.ITS[pivot.ITS == ""] <- NA   

pivot.ITS <- pivot.ITS %>% group_by(SampleID, kingdom, phylum, class, order, family, genus, species, ASV) %>% dplyr::summarize(value = sum(value))

phylum.ITS <- pivot.ITS %>% dplyr::select(SampleID, kingdom, phylum, value) %>% group_by(SampleID, kingdom, phylum) %>% dplyr::summarize(value = sum(value))

phylum.ITS <- phylum.ITS %>% pivot_wider(names_from = phylum, values_from = value)

phylum.ITS[c(3:11)] <- sapply(phylum.ITS[c(3:11)],as.numeric)
phylum.ITS[is.na(phylum.ITS)] <- 0

phylum.ITS <- merge(metadata, phylum.ITS, by = "SampleID")
```

```{r}
# make a longer table, this is easier to graph with (hence why I named it ggplot)
phylum.ggplot.ITS <- pivot_longer(phylum.ITS, cols = p__Dinophyta:'NA',names_to = "phylum", values_to = "value") %>% mutate(rel = value/sum(value))
```

```{r}
one.percent <- phylum.ggplot.ITS %>% dplyr::group_by(phylum) %>% dplyr::summarise_at(.vars = "rel", sum) %>% filter(rel < 0.01)
one.percent.vector <- phylum.ggplot.ITS %>% filter(phylum %in% one.percent$phylum)
`%notin%` <- Negate(`%in%`)
phylum.ggplot <- phylum.ggplot.ITS %>% filter(phylum %notin% one.percent$phylum)
one.percent.vector$phylum <- rep("< 1% Relative Abundance", nrow(one.percent.vector))


phylum.ggplot.ITS <- rbind(phylum.ggplot.ITS, one.percent.vector)
```

```{r}
# group phyla in order and choose the 10 most abundant 
phylum.group <- pivot.ITS %>% group_by(phylum) %>% dplyr::summarise(value = sum(value)) 
phylum.group <- phylum.group[order(-phylum.group$value),]
phylum.10 <- phylum.group[c(1:10),]
```

```{r}
phylum.10.plot <- ggplot(
    phylum.ggplot.ITS %>% filter(phylum %in% phylum.10$phylum),
    aes(fill = phylum, y = value, x = Treatment)
  ) + geom_bar(position = "fill", stat = "identity") + labs(y = "Relative Abundance") + theme_bw() + scale_fill_manual(values = pal) +
  theme(axis.text.x = element_text(
    angle = 45,
    vjust = 1,
    hjust = 1),legend.position = "right", text=element_text(size=20), axis.title.x = element_blank(), legend.title=element_blank()) + ggtitle("B.")
```

```{r}
png("figures/Experiment7/June_Revision_Figures /fungiphylum.png", res = 300, height = 40, width = 40, units = "cm")
phylum.10.plot
dev.off()
```

Are there phyla that differ between treatments?
```{r}
phylum.anova <- phylum.ggplot.ITS %>% group_by(phylum) %>%
  do(broom::tidy(TukeyHSD(aov(value ~ Location, data = .)))) %>%
  ungroup

phylum.anova.sig <- phylum.anova %>% filter(adj.p.value < 0.05) 

phylum.anova.sig 
```

```{r}
# remove ASVs that have no information 
pivot.ITS.genus <- ITS %>% filter(kingdom != "Unassigned") %>% pivot_longer(cols = c(BS1:NyTopR3), names_to = "SampleID")

# if there are blanks, these should be NA
pivot.ITS.genus[pivot.ITS.genus == ""] <- NA  
pivot.ITS.genus$value[is.na(pivot.ITS.genus$value)] <- 0

genus.ITS <- pivot.ITS.genus %>% group_by(SampleID, phylum, genus) %>% dplyr::summarize(value = sum(value))

genus.ITS <- genus.ITS %>% dplyr::select(SampleID, phylum, genus, value) %>% group_by(SampleID, phylum, genus) %>% dplyr::summarize(value = sum(value))

genus.ITS <- genus.ITS %>% pivot_wider(names_from = genus, values_from = value)

genus.ITS[c(3:136)] <- sapply(genus.ITS[c(3:136)],as.numeric)
genus.ITS[c(3:136)] [is.na(genus.ITS[c(3:136)])] <- 0

genus.ITS <- merge(metadata, genus.ITS, by = "SampleID")
```

```{r}
# make a longer table, this is easier to graph with (hence why I named it ggplot)
genus.ITS <- genus.ITS %>% filter(Treatment == "Nymphaea_Sunken") %>% pivot_longer(cols = g__Acremonium:g__Rozellomycota_gen_Incertae_sedis,names_to = "genus", values_to = "value") %>% mutate(rel = value/sum(value))
```

```{r}
# group phyla in order and choose the 10 most abundant 
genus.group <- genus.ITS %>% group_by(genus) %>% dplyr::summarise(value = sum(rel)) 
genus.group <- genus.group[order(-genus.group$value),]
```


Make table based on ASVs to then use as OTU and Tax Tables in phyloseq 

```{r}
otu.table <- ITS[,c(9:26)]
otu.table <- as.matrix(otu.table)
rownames(otu.table) <- ITS$ASV
tax.table <- ITS[,c(2:8)]
tax.table <- as.matrix(tax.table)
rownames(tax.table) <- ITS$ASV

otu.table <- otu_table(otu.table, taxa_are_rows = TRUE)
tax.table <- tax_table(tax.table)
sam.data <- as.matrix(metadata)
sam.data <- sample_data(metadata)
rownames(sam.data) <- metadata$SampleID
```

```{r}
ps <- phyloseq(otu.table, tax.table, sam.data)
random_tree = rtree(ntaxa(ps), rooted=TRUE, tip.label=taxa_names(ps))

ps = merge_phyloseq(ps,random_tree)
ps <- subset_taxa(ps, kingdom !="Unassigned")
ps <- subset_taxa(ps, phylum != "NA")
```
Plot richness and diversity 
```{r}
p = plot_richness(ps, x="Treatment", measures=c("Observed","Shannon", "Simpson")) + geom_point() + theme_bw() + geom_boxplot(aes(fill = Treatment)) + scale_fill_manual(values = c('#88CCEE','#882255', '#44AA99','#EE8866','#DDCC77','#332288')) + theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1, size = 20), legend.position = "none", axis.title.x = element_blank(), legend.title=element_blank(), text=element_text(size=20), plot.margin =margin(r = 30)) + ggtitle("A.")

p
```

Make a new dataframe with the ASVs from the pivot dataframe (leaves only for the venn diagram)
```{r}
leaves.only <- ITS %>% filter(kingdom != "Unassigned") %>% pivot_longer(cols = c(NuBotR1:NyTopR3), names_to = "SampleID")

leaves.only <- leaves.only %>% group_by(SampleID, kingdom, phylum, class, order, family, genus, species, ASV) %>% dplyr::summarize(value = sum(value))

ASV <- leaves.only %>% dplyr::select(SampleID, ASV, value) # 
ASV <- ASV %>% pivot_wider(names_from = ASV, values_from = value)
ASV[c(9:1138)] <- sapply(ASV[c(9:1138)],as.numeric)
ASV[c(9:1138)][is.na(ASV[c(9:1138)])] <- 0
ASV <- merge(metadata, ASV)
ASV.gp <- ASV %>% group_by(SampleID, Location, Plant, Treatment) %>% summarize_at(vars(ASV1107:ASV147), sum)
```

```{r}
ASV.long <- pivot_longer(ASV.gp, cols = ASV1107:ASV147, names_to = "ASV", values_to = "count")

y <- ASV.long %>% filter(Plant != "None") %>% dplyr::select(Treatment, ASV, count)

NuBot = y %>% filter(Treatment == "Nuphar_Sunken")  %>% filter(count >0) %>% dplyr::select(ASV) #476
NuTop = y %>% filter(Treatment == "Nuphar_Floating")  %>% filter(count >0) %>% dplyr::select(ASV) #427
NyBot = y %>% filter(Treatment == "Nymphaea_Sunken")  %>% filter(count >0) %>% dplyr::select(ASV) #371
NyTop = y %>% filter(Treatment == "Nymphaea_Floating")  %>% filter(count >0) %>% dplyr::select(ASV) #366


y <- rbind(NuBot, NuTop, NyBot, NyTop)

Treatment <- c(rep("Nu.Buried", 476), rep("Nu.Floating", 427), rep("Ny.Buried", 371), rep("Ny.Floating", 366))

y$Treatment <- Treatment

x <- list(NuS = y$ASV[1:476], NuF = y$ASV[477:903], NyS = y$ASV[904:1274], NyF = y$ASV[1275:1640])

```

```{r, echo=FALSE}
venn.e <- ggvenn(
  x, 
  fill_color = pal,
  stroke_size = 0.5, set_name_size = 3.5, show_percentage = TRUE,  text_size = 4) 

pdf("figures/Experiment7/NymphaeaNuphar_Figures_April2023/venn_ITS.pdf")
venn.f
dev.off()
```

Make heatmaps with ampvis 

```{r}
otu.table <- as.data.frame(ps@otu_table)
tax.table <- as.data.frame(ps@tax_table)

d <- amp_load(otutable = otu.table,
              metadata = metadata,
              taxonomy = tax.table)

amp_rarecurve(
  d,
  stepsize = 1000,
  color_by = "SampleID",
  facet_by = NULL,
  facet_scales = "fixed"
)

d.rare <-amp_rarefy(d, 15606)
```

```{r}
tax_vector <- c("g__uncultured", "NA")
sam_vector <- c()
d.known.genera <- amp_filter_taxa(d.rare, 
                                  tax_vector = tax_vector, 
                                  remove = TRUE)

d.known.genera <- amp_filter_samples(d.known.genera, 
                                  Type == "Plant")

genus.heatmap.f <- amp_heatmap(data = d.rare, 
             tax_aggregate = "Genus",
             tax_add = "Phylum",
             group_by = c("Treatment"),
             tax_show = 30,
             plot_colorscale = "log10", 
             plot_values = FALSE)
genus.heatmap.f <- genus.heatmap.f + ggtitle("B")+ theme(text = element_text(size = 12))
```

```{r}
pdf("figures/Experiment7/NymphaeaNuphar_Figures_April2023/heatmap_ITS.pdf", width = 20, height = 20)
genus.heatmap.f
dev.off()
```

Determine differences in richness and diversity 
```{r}
alpha <- amp_alpha_diversity(d.rare)

rich.lm <- lm(ObservedOTUs ~ Plant, data = alpha %>% filter(Plant != "None"))
rich.aov <- aov(rich.lm)
TukeyHSD(rich.aov)
summary(rich.aov)

div.lm <- lm(Shannon ~ Location, data = alpha %>% filter(Plant != "None"))
div.aov <- aov(div.lm)
summary(div.aov)

div.lm <- lm(Simpson ~ Location, data = alpha%>% filter(Plant != "None"))
div.aov <- aov(div.lm)
summary(div.aov)
```

Look for ASVs that are overrepresented in floating or buried leaves using Deseq
```{r}
# ps1 <- subset_samples(ps, Plant != "None")
# wh0 = genefilter_sample(ps1, filterfun_sample(function(x) x > 5), A=0.5*nsamples(ps1)) # removes low abundance pathways
# GP1 = prune_taxa(wh0, ps1)
# GP1 = transform_sample_counts(GP1, function(x) 1E6 * x/sum(x))
# mb <- GP1
```

```{r}
# # First, we will convert the sequence count data from our phyloseq object into the proper format for DESeq2
# mb.dds <- phyloseq_to_deseq2(mb, ~ Location)
# 
# # Next we need to estimate the size factors for our sequences
# gm_mean = function(x, na.rm=TRUE){
#     exp(sum(log(x[x > 0]), na.rm=na.rm) / length(x))
# }
# geoMeans = apply(counts(mb.dds), 1, gm_mean)
# mb.dds = estimateSizeFactors(mb.dds, geoMeans = geoMeans)
# 
# # Finally, we can run the core DESeq2 algorithm
# mb.dds = DESeq(mb.dds, fitType="local")
```

```{r}
# # Create a new dataframe from the results of our DESeq2 run
# mb.res = results(mb.dds)
# 
# # Reorder the sequences by their adjusted p-values
# mb.res = mb.res[order(mb.res$padj, na.last=NA), ]
# 
# # Set your alpha for testing significance, and filter out non-significant results
# alpha = 0.05
# mb.sigtab = mb.res[(mb.res$padj < alpha), ]
# 
# mb.res = cbind(as(mb.res, "data.frame"), as(tax_table(mb)[rownames(mb.res), ], "matrix"))
# 
# # Add taxonomy information to each sequence
# mb.sigtab = cbind(as(mb.sigtab, "data.frame"), as(tax_table(mb)[rownames(mb.sigtab), ], "matrix"))
# head(mb.sigtab)
# 
# mbsigtab.fungus <- fwrite(mb.sigtab, "export/deseqfungus.csv")
```

```{r}
# mb.sigtab$group<- ifelse(mb.sigtab$log2FoldChange < 0, 'buried','floating')
# mb.sigtab$color <- ifelse(mb.sigtab$log2FoldChange < 0, '#882255','#88CCEE')
# mb.ns <- mb.res %>% filter(padj > 0.05)
# 
# volcano.plot.f <- ggplot(mb.sigtab, aes(x = log2FoldChange, y = -log10(padj))) + geom_point(color = mb.sigtab$color, size = 4) + geom_hline(aes(yintercept =-log10(0.05)), linetype = "dashed") + theme_bw() + geom_point(data = mb.ns, mapping = aes(x = mb.ns$log2FoldChange, y = -log10(mb.ns$padj)), color = "gray", size = 4)+ theme(text=element_text(size=20)) 
```

```{r}
# pdf("figures/Experiment7/NymphaeaNuphar_Figures_April2023/volcanoplot_ITS.pdf")
# volcano.plot.f
# dev.off()
```

```{r}
library(patchwork)

png("figures/Experiment7/NymphaeaNuphar_Figures_April2023/fungusfigures_revision.png", width = 39, height = 24, units = 'cm', res = 300)
p + pcoa
dev.off()
```
















